---
title: "Homework 4 Questions 2-12"
output: html_document
---

##### JULIA'S COMMENTS #####
Susan, good work! Here are some comments to improve your code. 
* You don't make any comments on your code, and it makes it a little difficult to follow. It's always helpful if someone is going to read over your code to make comments to help them follow your thought process. 
* It doesn't appear that you loaded all the packages that you need for this assignment, specifically tidyverse. 
* To the above point, you have code that is outside of chunks, without the code being in a chunk, it makes it diffcult to quickly run and troubleshoot because you would have to manually run the line or copy and paste it into the console. It's best to keep all the code in chunks. You can go to "Code" and then "Insert Chunk" in the code above. 
* I couldn't get your function to run, but it doesn't look rigid or fragile. If you needed to search for data that didn't have "san" or "santa" in it, you definitely could!

Overall, you could definitely clean up your code with comments and containing all your code in chunks. Keep up the good work. 

##### End of Julia's Comments #####


Question 2

What class is o3.filelist? What does it contain?

Answer:

The o3.filelist is a list of text files that contain ozone data for a variety of lication within California on a hourly basis speaprated into years ranging from 1980 to 2011.  

Question 3

Using ~ 1 sentence per line in the above code, explain what each line in the code is doing.

Answer:

library(tidyverse)
setwd("ca_ozone")
```{r}
require(readr)
o3.filenames <- list.files(pattern = ".txt")
o3.filelist <- lapply(o3.filenames, read_delim, delim = "|")
names(o3.filelist) <- gsub(".txt","", o3.filenames)
```

You first tell R to set your working directory to the ca.ozone folder.  You than tell R to require the readr package so it can use the required functions to carry out the remaining lines.  You create a file list by looking for all the files that have the ".txt" extension in them.  Since they are text files with no defined columns and rows, you want to clean it up with lapply creating a spreadsheet by separating each chunk of information that are wrapped with a "|".  

Question 4

Rewrite the code above using the stringr package insead of grep{base}.

Answer:

```{r}
which(str_detect(o3.filelist, ".txt"))
str_replace(o3.filelist, ".txt", "")
```

Question 5

Rewrite the code above using traditional object-based R programming instead of the piping operator.

library(data.table)
library(tidyverse)
daily <- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), date) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
daily

Answer:

install.packages("data.table")
```{r}
#library(data.table)
bind<-rbindlist(o3.filelist)
group<-group_by(bind, site=as.factor(site))
summarize(group = mean(obs, na-rm=TRUE))

```

Question 6

Summarize the o3 data above by site and by month and by year using a piping operator (the monthly mean o3 for each site for each year).

<<<<<<< HEAD
Question 7

Challenge! Ozone pollution actually follows a very strong diurnal pattern. How would you summarize the daily data from above in a better way to capture that diurnal pattern?

```{r}
colnames(location)[1] <- "site"
daily.site <- daily %>%
  left_join(location, by = "site")
daily.site

```

Answer:


=======
>>>>>>> 9d2155f73666a2605b266b3b364f2ef84e18c7cb
Answer:

```{r}
monthly <- o3.filelist %>%
  rbindlist() %>%
  mutate(year = format(date, "%Y"),month = format(date, "%m")) %>%
  group_by(site = as.factor(site),year, month) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
monthly
```

<<<<<<< HEAD
```{r}
hourly <- o3.filelist 
  group_by_(o3.filelist, start_hour) 
  summarize(o3 = mean(obs, na.rm = TRUE))
)

```


=======
>>>>>>> 9d2155f73666a2605b266b3b364f2ef84e18c7cb
Question 8

How many site names in the CA air quality location dataset “Site Name” contain “San” or “Santa?”.

Answer:

library(readxl)
location <- read_excel("location.xls")
View(location)

```{r}
str_detect(location, "San")
str_which(location, "San") #just went ahead and added the list of numbers here (Site names with "San" or "Santa" equals 95)
str_count(location, "San")
str_length(location)
```

Question 9:

Identify the number of sites that do not have a complete address (full street address and zip code)

Answer:

```{r}
str_which(location$Address, "Address Not Known")
str_which(location, "Location Approximate")
str_which(location$'Zip Code', "\\b..\\b") #incomplete Zip Code (only 2 digits?)

sum(is.na(location$Address))
sum(is.na(location$`Zip Code`))
length(unique(location[is.na(location$Address) | is.na(location$`Zip Code`),]$Site))

```

<<<<<<< HEAD
Question 10

How does a semi join differ from an inner join?

Answer:

Inner join will return one row of x for each matching row of y while semi join never duplicates the rows of x.  

Question 11

Write a function to calculate the annual mean, median, max and min of all sites that have “San” or “Santa” in their name.

```{r}
Stats <- function(x,y,z){
  group_by(daily.site, site = as.factor(site))
  inner_join(filter(loc, grepl(paste(c(y,z), collapse="|"), loc$`Site Name`)), by = "site")
                  transform(daily.site, year = format(date, "%Y")) 
    group_by(daily.site, site,year) 
   summarize(annual_mean = mean(obs, na.rm = TRUE), annual_median = median(obs, na.rm = TRUE),annual_max = max(obs, na.rm = TRUE),annual_min = min(obs, na.rm = TRUE) )
    annual
    }

Stats(str_detect(daily.site),"San","Santa") 
  

```


